KidsAIR wood stove grades and usage

### 2020-12-09 stove_grade_usage_cleaning.Rmd
main analysis updates

>>>>

kids_kw_filtered <- kids_kw_clean %>% 
  left_join(kids_sampling_dates, by = c("area", "home_winter_id")) %>% 
  mutate(date_diff = as.duration(interval(intervention_date, kw_date)),
         date_diff = as.numeric(date_diff)/86400) %>% 
  left_join(filter_units, by = c("area", "home_winter_id")) %>% 
  distinct(area, home_winter_id, .keep_all = TRUE) %>% 
  mutate(multiplier = if_else(filter_type == "Honeywell" & treatment_assigned == "Placebo",
                              2.04, 0),
         multiplier = if_else(filter_type == "Honeywell" & treatment_assigned == "Filter",
                              4.224, multiplier),
         multiplier = if_else(filter_type == "Small Filtrete" & treatment_assigned == "Placebo",
                              0.888, multiplier),
         multiplier = if_else(filter_type == "Small Filtrete" & treatment_assigned == "Filter",
                              1.896, multiplier),
         multiplier = if_else(filter_type == "Large Filtrete" & treatment_assigned == "Placebo",
                              1.896, multiplier),
         multiplier = if_else(filter_type == "Large Filtrete" & treatment_assigned == "Filter",
                              3.48, multiplier),
         multiplier = if_else(filter_type == "Winix" & treatment_assigned == "Placebo",
                              0.0144, multiplier),
         multiplier = if_else(filter_type == "Winix" & treatment_assigned == "Filter",
                              0.48, multiplier)) %>% 
  mutate(kw_expected = date_diff*multiplier,
         kw_perc_exp = kw_hours/kw_expected*100)

kw_perc_exp_summary <- kids_kw_filtered %>% 
  left_join(pm_data, by = c("area", "home")) %>% 
  filter(!is.na(kw_perc_exp)) %>% 
  filter(kw_perc_exp < 30000) %>% 
  #filter(area == "WMT") %>% 
  group_by(filter_type, treatment_assigned) %>% 
  summarize("Mean KW % Exp" = mean(kw_perc_exp, na.rm = TRUE),
            "SD KW % Exp" = sd(kw_perc_exp, na.rm = TRUE),
            "N KW % Exp" = n(),
            "Min KW % Exp" = min(kw_perc_exp, na.rm = TRUE),
            "Med KW % Exp" = median(kw_perc_exp, na.rm = TRUE),
            "Max KW % Exp" = max(kw_perc_exp, na.rm = TRUE),
            "Mean PM" = mean(pm_mean_sampling_period, na.rm = TRUE),
            "Min PM" = min(pm_mean_sampling_period, na.rm = TRUE),
            "Med PM" = median(pm_mean_sampling_period, na.rm = TRUE),
            "Max PM" = max(pm_mean_sampling_period, na.rm = TRUE))
kw_perc_exp_summary
